Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-08-28 Paper.Rmd
jrny conts
it does

---
title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
bibliography: references.bib
link-citations: yes
csl: ieee.csl
output:
  bookdown::pdf_document2: 
    fig.caption: yes
    includes:
      in_header: non-float-fig.tex
    toc_depth: 4
---

@@

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages both for sellers and buyers. One of the positive perks is Online Customer Reviews (OCR). Online Customer Reviews come in the form of electronic word-of-mouth @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010. OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @nelson1970 . Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

However, the increased rate of electronic commerce activity also created an abundance of product reviews on the internet. The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021]. Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of customer reviews. Additionally, not all reviews have the same informativeness level @pan2011. Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost. To make the understanding of a "helpful review" more clear it can be defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.

Since OCR don't share the same level of informativeness and usefulness @pan2011, most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews. On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button. In this paper, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable @ahmad2015.

The research on perceived helpfulness is still growing. In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature @hunter1991. In this case, the study on perceived helpfulness is not an exception. Because of this reason, more empirical studies on perceived helpfulness are required. This paper aims to add one more perspective to growing literature of customer reviews and review helpfulness.

This study uses secondary data. The reviews were collected from two websites. Namely, IMDB and BestBuy. The data was scrapped with Selenium Webdriver for Python @python3. Over 400,000 reviews and their meta data were gathered initially. After the data transformation process the final sample size was over 23,000.

-   Briefly talk about the results.

-   Outline the paper

@@

The research on Online Customer Reviews could be considered to have two main branches. One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012]. The other branch is concerned with rather behavioral or psychological outcomes and focuses on perceived helpfulness only. Of course, the boundary between these two branches are somewhat blurry and same independent variables were used to explain both helpfulness and sales. Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales. Many other papers used perceived helpfulness to explain sales as well [@ghose2011; @lee2018]. Thus, these two branches are inter-connected with each other. This paper tries to understand behavioral aspect.

Many independent variables and their relationship between perceived helpfulness were examined by researchers. Hong et al. (2017) @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group tries to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.). [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. Ghose et al. (2011) @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. The choice of the variables is of course heavily dependent on the data itself. In this paper, only review-related predictors were examined.

@@

Review Rating (Review Extremity) is another important identifier of perceived helpfulness. This is usually the star rating on a 1-5 or 1-10 scale and resembles the evaluation of the reviewer for a given product. It's effect on perceived helpfulness is rather divergent in the literature. A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness. Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006]. In other studies, linear positive relationship was found. In other words, positively rated reviews are more useful [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020]. There are also results that support negative linear relationship[@chua2014] and no effect at all[@hong2017].

Review Age is an indicator of how long the time passed after a review published on a web site. On some papers the opposite of Review Age, Review Freshness could be employed as well. Different effects on perceived helpfulness were also observed by researchers. Some researchers discussed that a timely review is very important at conveying the true information about a certain product [@liu2014; @li2019; @zhou2019]. Others discussed that some web sites promotes newer reviews and because of that more recent reviews are more helpful [@lee2014; @choi2020; @wu2021].

The counts of negative or positive words out of total word count (the proportion of negative and positive words) were employed by a handful of studies [@baek2012; @kuan2015]. These metrics can measure the sentiment of the review itself. They are usually different than Review Extremity. In most cases Review Extremity and Review Sentiment (Valence) don't match @zhang2011. Both Baek et al. (2012) @baek2012 and Kuan et al. (2015) @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness. The relationship between the proportion of positive words and perceived helpfulness was found to be negative @kuan2015.

The classification of Experience and Search goods plays a moderating role in the literature [@mudambi2010; @sun2019; @baek2012; @lee2016]. Some of these studies showed that Review Length has a greater effects for search products than experience products [@mudambi2010; @baek2012; @lee2016]. These findings suggest that search goods can be evaluated in a more objective way than experience goods. The moderating effect of product type on Review Extremity, on the contrary, is disputable. Mudambi (2010) @mudambi2010 showed that moderate reviews are more helpful for experience products than search products. Baek (2012) @baek2012 and Lee (2016) @lee2016 had the opposite results which indicated that more extreme reviews (negative or positive) is more helpful more search goods than experience goods.

@@

Nelson (1970) [@nelson1970] differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. A product's Total Cost consists of both Search Cost and Product Cost. This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.

To explain it in a more generalized way, let's also define what "search" is. Nelson (1970) [@nelson1970] defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search". People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search. This is why search is costlier for Experience Goods. For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it. Even though a car has experience attributes, with this logic it is considered as a search good @klein1998.

@@

Humans tend to care about losses more than same amount of gains. Losing 100\$ is psychologically much more impactful than finding 100\$. This behavior is best explained by "loss aversion" from Behavioral Economics. [@kahneman1979; @schindler2017]. Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses @herr1991.

Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than positive ones. --, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones. --, higher negative dominance -- A combination of equally negative and positive cues results in more negative impressions. --, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones. --[@rozin2001; @sen2007; @eslami2018].

# Research Methodology

@@

The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 @python3. The scraper got the customer reviews from IMDB and BestBuy. The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America. Both websites host a great amount of online reviews. After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].

@@

BestBuy is a very big electronics retailer and because of this the website offers a sizable number of OCR for search goods. Contrary to experience goods, search goods usually have more objectively quantifiable traits. For example, resolution or screen size of a TV, RAM or GPU of a Laptop, storage or battery lifetime of a Smart Phone. Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019]. Therefore, search goods data was collected from BestBuy.

@@

From IMDB reviews of 22 movies were collected as experience goods. In total 22 movies account for 31,863 reviews. From BestBuy, total of 383,357 reviews were collected as search goods. Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones. However, in the data there are many reviews that were never voted. To make sure that I am analyzing reviews that were actually read by people, I set a threshold for Total Reviews as five. In other words, reviews that had less than 5 Total Votes were removed from the analysis data[@choi2020; @baek2012]. At the very end, the analysis data was consisted of 15,024 observations for experience goods and 8,042 observations for search goods. It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times. Most of the search product reviews aren't getting voted and even maybe they aren't getting read at all. This might support the idea that people form more homogeneous opinions about search goods @hong2014. Once a helpful review is written most of the other reviews become redundant since other reviews most likely conveys similar information. On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times. This might be because people form heterogeneous opinions about experience goods @hong2014.

@@

Hong et al. (2014) [@hong2014; @sun2019] states that consumers likely to form homogeneous opinions about search goods. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. One person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

For both search and experience goods the bi-modality of the distributions can be observed on Figure \@ref(fig:Search-Rating) (A) and Figure \@ref(fig:Experience-Rating) (A) respectively. Hu et al. @hu2006 also pointed out a similar distribution concerning Online Product Reviews. This might mean that consumers usually tend to write product reviews when they are extremely happy or unhappy with the product.

@@

The exponential distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A). This means that reviews become less prevalent as they get longer. This might suggest logarithmic transformation which can increase the model fit. For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).

The bivariate relationship between the number of words and Helpfulness seems to be varying for different product types. For Search goods on Figure \@ref(fig:Search-Length) (C) there is a clear positive relationship [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, this positive relationship appears to stop at a threshold[@schindler2012; @huang2015; @baek2012; @kuan2015; @eslami2018]. With this in mind, logarithmic transformation might make more sense (see Figure \@ref(fig:Search-Length) (D)) for modelling purposes. For Experience goods, on the other hand, there seems to be a weak negative relationship or no relationship at all (see Figure \@ref(fig:Experience-Length) (C) and (D)).

@@

Negative words were derived by using NRC Word-Emotion Association Lexicon @Mohammad13. A lexicon is basically a dictionary of words. These words might have similar emotions or sentiments. In this case, negative words lexicon was used in order to engineer this variable. A sample of negative words from the lexicon can be observed below.

@@

```{r Correlations, fig.cap="Correlations between Independent Variables.", fig.height=8}
p1 <- search_goods %>% 
  select(Rating, Word_Count, Freshness, positive, negative, Total_Vote) %>% 
  rename(Proportion_Positive = positive) %>% 
  rename(Proportion_Negative = negative) %>% 
  mutate(Word_Count = log10(Word_Count),
         Total_Vote = log10(Total_Vote)) %>% 
  ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
         high = "darkred", label_round = 2, layout.exp = 1)+
  labs(title = "Search Goods")+
  theme_void()

p2 <- movies_data %>% 
  select(Rating, Word_Count, Freshness, positive, negative, Total_Vote) %>% 
  rename(Proportion_Positive = positive) %>% 
  rename(Proportion_Negative = negative) %>% 
  mutate(Word_Count = log10(Word_Count),
         Total_Vote = log10(Total_Vote)) %>% 
  ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
         high = "darkred", label_round = 2, layout.exp = 1)+
  labs(title = "Experience Goods")+
  theme_void()

@@

Korfiatis et al. (2012) @korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers. This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006]. As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful. This extremeness has more objective nature for Search Goods since there are more ways to express pleasantness or unpleasantness for a particular product. For instance a bad design in a laptop might cause fans to make much more noise than they should normally do. This information along with a very low rating may signal there are some inherent problems with that particular product, making the feedback more helpful. On the other hand, for Experience Goods and in this specific case movies, opinions for a given product might be much more subjective. For example, a reviewer might find a movie "childish" and give it one star, the other might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness. Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process @hoch1989. In other words, prior expectations play a bigger role in decision making process for experience goods. Therefore it is hypothesized that:

@@

In order to decrease the uncertainty, search costs must be reduced. In \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods @hong2014 . This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions @hong2014. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. However, since there are other ways to objectively evaluate a movie, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

As it was mentioned in \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses. Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses. Guo et al. (2019) @guo2019 found out that people spent more time when evaluating negative reviews. This may suggest a linear interaction between Review Extremity and Review Length. Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low. And when a review is longer it is more helpful for negatively rated reviews than positively rated reviews. In this case, it is hypothesized that:

@@

--- --- --- ---

>>>>

---
title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
bibliography: references.bib
link-citations: yes
output:
  bookdown::pdf_document2: 
    fig.caption: yes
    includes:
      in_header: non-float-fig.tex
    toc_depth: 4
---

@@

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages both for sellers and buyers. One of the positive perks is Online Customer Reviews (OCR). Online Customer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010]. OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] . Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

However, the increased rate of electronic commerce activity also created an abundance of product reviews on the internet. The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021]. Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of customer reviews. Additionally, not all reviews have the same informativeness level [@pan2011]. Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost. To make the understanding of a "helpful review" more clear it can be defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].

Since OCR don't share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews. On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button. In this study, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].

The research on perceived helpfulness is still growing. In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature [@hunter1991]. In this case, the study on perceived helpfulness is not an exception. Because of this reason, more empirical studies on perceived helpfulness are required. This paper aims to add one more perspective to the growing literature of customer reviews and review helpfulness.

This study uses secondary data. The reviews were collected from two websites. Namely, IMDB and BestBuy. The data was scrapped with Selenium Webdriver for Python [@python3]. Over 400,000 reviews and their meta data were gathered initially. After the data transformation process the final sample size was over 23,000. Then this data was subjected to empirical tests. It was found out that consumers usually find extreme reviews more helpful than neutral ones. Furthermore, consumers prefer longer reviews when reviews are rated negatively. On the contrast, positive reviews with fewer words were deemed more helpful by readers on the average. These effects were further moderated by product types, namely, Search and Experience goods.

The plan of this study is outlined as the following. In the next section, the literature on the subject of Review Helpfulness is going to be presented. In the third section, the related theories which would make the understanding of the consumer behavior and review helpfulness will be laid out. Next, the data and the research methodology are going to be introduced. The results will be shared in the fifth section. In the last section the results are going to be discussed and the study is going to be concluded.

@@

The research on Online Customer Reviews could be considered to have two main branches. One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012]. The other branch is concerned with rather behavioral or psychological outcomes and focuses on perceived helpfulness only. The boundary between these two branches are somewhat blurry and the same independent variables were used to explain both helpfulness and sales. Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales. Many other papers used perceived helpfulness to explain sales as well [@ghose2011; @lee2018]. Thus, these two branches are inter-connected with each other. This paper tries to understand behavioral aspect of the review helpfulness rather than its effects on sales.

Many independent variables and their relationship between perceived helpfulness were examined by researchers. @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group try to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.). [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. The choice of the variables is heavily dependent on the data itself. In my paper, only review-related predictors were examined because the data which is available for this study only allows for review-related variables.

@@

Review Rating (Review Extremity) is another important identifier of perceived helpfulness. This is usually the star rating on a 1-5 or 1-10 scale and resembles the evaluation of the reviewer for a given product. Its effect on perceived helpfulness is rather divergent in the literature. A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness. Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006]. In other studies, linear positive relationship was found. In other words, positively rated reviews are more useful [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020]. There are also results that support negative linear relationship[@chua2014] and no effect at all[@hong2017].

Review Age is an indicator of how long the time passed after a review published on a web site. On some papers the opposite of Review Age, Review Freshness (Recency) could be employed as well. Different effects on perceived helpfulness were also observed by researchers. Some researchers discussed that a timely review is very important at conveying the true information about a certain product [@liu2014; @li2019; @zhou2019]. Others discussed that some web sites promotes newer reviews and because of that more recent reviews are more helpful [@lee2014; @choi2020; @wu2021].

The counts of negative or positive words out of total word count (the proportion of negative and positive words) were employed by a handful of studies [@baek2012; @kuan2015]. These metrics can measure the sentiment of the review itself. They are usually different than Review Extremity. In most cases Review Extremity and Review Sentiment (Valence) don't match [@zhang2011]. @baek2012 and @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness. The relationship between the proportion of positive words and perceived helpfulness was found to be negative [@kuan2015].

The classification of Experience and Search goods plays a moderating role in the literature [@mudambi2010; @sun2019; @baek2012; @lee2016]. Some of these studies showed that Review Length has a greater effect for search products than experience products [@mudambi2010; @baek2012; @lee2016]. These findings suggest that search goods can be evaluated in a more objective way than experience goods. There is also moderating effect of product type on Review Extremity. @mudambi2010 showed that moderate reviews are more helpful for experience products than search products. @baek2012 and @lee2016 had the results which indicated that more extreme reviews (negative or positive) is much more helpful for search goods than experience goods.

Many different types of research methodologies were employed in the literature of the Review Helpfulness. To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014]. Some of these studies also shared Ordinary Least Squares results alongside with the Tobit Regression results for the purpose of benchmarking [@mudambi2010; @kuan2015; @choi2020]. Ordinary Least Squares were also used as a main empirical methodology in some papers [@liu2014; @ghose2006; @lee2016]. Furthermore, Ordinary Least Squares was employed in a hierarchical manner as well [@baek2012]. Some other studies employed Multi-Level Regression models in order to deal with potential biases [@ghose2011; @wu2021; @kuan2015]. In a rare case Ordinal Logistic Regression was one of the methods that was used to explain the determinants of the review helpfulness [@cao2011]. Predictive methods such as Neural Networks were used to understand the components of a helpful review as well [@lee2014]. One paper attacked the problem of the review helpfulness with three methods, namely, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].

@@

@nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981]. Search Attributes are the qualities that can be assessed before purchase. On the contrary, Experience Attributes can only be assessed by using the product itself, in other words evaluation is only possible after purchase. A single good can have both search and experience attributes. Depending on its dominant attributes the good can be classified as Search or Experience. A product's Total Cost consists of both Search Cost and Product Cost. This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.

To explain it in a more generalized way, let's also define what "search" is. @nelson1970 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search". People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search. This is why search is costlier for Experience Goods. For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it. Even though a car has experience attributes, with this logic it is considered as a search good [@klein1998].

@@

Humans tend to care about losses more than same amount of gains. Losing 100\$ is psychologically much more impactful than finding 100\$. This behavior is best explained in "loss aversion" from behavioral economics. [@kahneman1979; @schindler2017]. Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses [@herr1991].

Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than the positive ones. --, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones. --, higher negative dominance -- A combination of equally negative and positive cues results in more negative impressions. --, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones. --[@rozin2001; @sen2007; @eslami2018].

# The Data and Research Methodology

@@

The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 [@python3]. The scraper got the customer reviews from IMDB and BestBuy. The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America. Both websites host a great amount of online reviews. After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].

@@

BestBuy is a very big electronics retailer and this is why the website offers a sizable number of OCR for search goods. Contrary to experience goods, search goods usually have more objectively quantifiable traits. For example, resolution or screen size of a TV, RAM or GPU of a Laptop, storage or battery lifetime of a Smart Phone. Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019]. Therefore, search goods data was collected from BestBuy.

@@

From IMDB reviews of 22 movies were collected as experience goods. In total, 22 movies account for 31,863 reviews. From BestBuy, total of 383,357 reviews were collected as search goods. Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones. However, in the data there are many reviews that were never voted. To make sure that I am analyzing reviews that were actually read by people, I set a threshold for Total Reviews as five. In other words, reviews that had less than 5 Total Votes were removed from the analysis data [@choi2020; @baek2012]. At the very end, the analysis data was consisted of 15,024 observations for experience goods and 8,042 observations for search goods. It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times. Most of the search product reviews aren't getting voted and even possible that they aren't getting read at all. This might support the idea that people form more homogeneous opinions about search goods [@hong2014]. Once a helpful review is written most of the other reviews become redundant since other reviews most likely conveys similar information. On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times. This might be because people form heterogeneous opinions about experience goods [@hong2014].

@@

@hong2014 states that consumers likely to form homogeneous opinions about search goods [@sun2019]. On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods. Intuitively, what these histograms show is the same. For instance, positive or negative attributes of search goods can be expressed in a limited number of ways. The storage space of a phone might be small or CPU of a laptop might not be fast as expected. Thus, one good review is enough to reveal the quality of a product. I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search). In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%. This might be because evaluation process of movies is rather subjective. One person might not like Spider-Man: Homecoming and another would love it. This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.

@@

For both search and experience goods the bi-modality of the distributions can be observed on Figure \@ref(fig:Search-Rating) (A) and Figure \@ref(fig:Experience-Rating) (A) respectively. @hu2006 also pointed out a similar distribution concerning Online Product Reviews. This might mean that consumers usually tend to write product reviews when they are extremely happy or unhappy with the product.

@@

The exponential distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A). This means that reviews become less prevalent as they get longer. This might suggest logarithmic transformation can increase the model fit. For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).

The bivariate relationship between the number of words and Helpfulness seems to be varying for different product types. For Search goods on Figure \@ref(fig:Search-Length) (C) there is a clear positive relationship [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, this positive relationship appears to stop at a threshold [@schindler2012; @huang2015; @baek2012; @kuan2015; @eslami2018]. With this in mind, logarithmic transformation might make more sense (see Figure \@ref(fig:Search-Length) (D)) for modelling purposes. For Experience goods, on the other hand, there seems to be a weak negative relationship or no relationship at all (see Figure \@ref(fig:Experience-Length) (C) and (D)).

@@

Negative words were derived by using NRC Word-Emotion Association Lexicon [@Mohammad13]. A lexicon is basically a dictionary of words. These words might have similar emotions or sentiments. In this case, negative words lexicon was used in order to engineer this variable. A sample of negative words from the lexicon can be observed below.

@@

The relatively high positive/negative correlation between the Review Rating and Positive/Negative word proportions might give a hint about the usefulness of the lexicon. As the Review Rating gets higher the review contains more positive words and, on the other hand, low rated reviews have more negative words in them. This makes sense intuitively.

```{r Correlations, fig.cap="Correlations between Independent Variables.", fig.height=8}

p1 <- search_goods %>% 
  select("Review Rating" = Rating,
         "Review Length" = Word_Count, Freshness,
        "Positive Proportion" = positive,
        "Negative Proportion" = negative,
        "Total Votes" = Total_Vote) %>% 
  mutate(`Review Length` = log10(`Review Length`),
         `Total Votes` = log10(`Total Votes`)) %>% 
  ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
         high = "darkred", label_round = 2, layout.exp = 1)+
  labs(title = "Search Goods")+
  theme_void()

p2 <- movies_data %>% 
  select("Review Rating" = Rating,
         "Review Length" = Word_Count, Freshness,
        "Positive Proportion" = positive,
        "Negative Proportion" = negative,
        "Total Votes" = Total_Vote) %>% 
  mutate(`Review Length` = log10(`Review Length`),
         `Total Votes` = log10(`Total Votes`)) %>% 
  ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
         high = "darkred", label_round = 2, layout.exp = 1)+
  labs(title = "Experience Goods")+
  theme_void()

@@

@korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers. This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006]. As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful. This extremeness has more objective nature for Search Goods since there are fewer ways to express pleasantness or unpleasantness for a particular product. For instance a bad design in a laptop might cause fans to make much more noise than they should normally do. This information along with a very low rating may signal there are some inherent problems with that particular product, making the feedback more helpful. On the other hand, for Experience Goods and in this specific case movies, opinions for a given product might be much more subjective. For example, a reviewer might find a movie "childish" and give it one star, the other might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness. Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process [@hoch1989]. In other words, prior expectations play a bigger role in decision making process for experience goods. Therefore it is hypothesized that:

@@

In order to decrease the uncertainty, search costs must be reduced. In \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. However, since there are other ways to objectively evaluate a movie, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

As it was mentioned in \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses. Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses. @guo2019 found out that people spent more time when evaluating negative reviews. This may suggest a linear interaction between Review Extremity and Review Length. Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low. And when a review is longer it is more helpful for negatively rated reviews than positively rated reviews. In this case, it is hypothesized that:

@@

------------------------------------------------------------------------
